A weighted sampling algorithm for the design of RNA sequences with targeted secondary structure and nucleotide distribution

### 2013-04-19 ISMB/Camera/Waldispuhl.337.tex
added figures pgf -> pdf (1,2)
moved fig , redid fig time

\begin{figure*}
\resizebox{\linewidth}{!}{\input{Waldispuhl.337.fig.1.pgf}}
\caption{Stochastic backtrack procedure for a given substructure $\Struct$: Either the first position is left unpaired (top), a base-pair is formed between the two extremities, stacking onto an exterior base-pair (middle), or paired without creating a stacking, defining two regions on which subsequent recursive calls are needed (bottom). For the empty structure (omitted here), the empty sequence is returned. Positions indicated in red are assigned at the current stage of the backtrack.\label{fig:stochastic}}
\end{figure*}

@@

\begin{figure}
\resizebox{\linewidth}{!}{\input{Waldispuhl.337.fig.2.pgf}}
\caption{General workflow of our adaptive sampling algorithm~\protect\citep{Waldispuhl2011}.}
\label{fig:workflow}
\end{figure}

@@

\subsection{Postprocessing unpaired regions: A local/global (glocal) hybrid approach}
\label{subsec:glocal_method}
Due to our simplified energy model, unpaired regions are not subject to design constraints other than the \GCContent, leading to modest probabilities for refolded design candidates to match the targeted structure. To improve these performances and test the complementarity  of our global sampling approach with previous contributions based on local search, we used the \RNAinverse software to redesign unpaired regions. We specified a constraint mask to prevent stacking base-pairs from being modified and, whenever necessary, reestablished their content {\em a posteriori}, as \RNAinverse has been witnessed to take some liberties with constraints masks. As shown in Table~\ref{table:impact_on_gc} (Supplementary material), this postprocessing does not drastically alter the \GCContent, so the glocal approach reasonably addresses the constrained \GCContent design problem.

@@

 \begin{figure*}[ht!]
 	\centering
	\includegraphics[width=\textwidth]{{Waldispuhl.337.fig.4}.pdf}
	\caption{Number of secondary structures per bin, according to our three clustering criteria.}
	\label{fig:bins}
 \end{figure*}

@@

\begin{figure}[ht!]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{{Waldispuhl.337.fig.5}.pdf}
  \end{center}
  \caption{Overall \GCContent distribution for sequences designed using \RNAinverse, \INFORNA, \NUPACK and \frankenstein folding in the desired structure.}
  \label{fig:gcdist}
\end{figure}

>>>>

\begin{figure}
%\resizebox{\linewidth}{!}{\input{{Waldispuhl.337.fig.2}.pdf}}
  \centering
  \includegraphics[width=0.45\textwidth]{{Waldispuhl.337.fig.1}.pdf}
\caption{General workflow of our adaptive sampling algorithm~\protect\citep{Waldispuhl2011}.}
\label{fig:workflow}
\end{figure}

\begin{figure*}
%\resizebox{\linewidth}{!}{\input{{Waldispuhl.337.fig.1}.pdf}}
  \centering
  \includegraphics[width=\textwidth]{{Waldispuhl.337.fig.2}.pdf}
\caption{Stochastic backtrack procedure for a given substructure $\Struct$: Either the first position is left unpaired (top), a base-pair is formed between the two extremities, stacking onto an exterior base-pair (middle), or paired without creating a stacking, defining two regions on which subsequent recursive calls are needed (bottom). For the empty structure (omitted here), the empty sequence is returned. Positions indicated in red are assigned at the current stage of the backtrack.\label{fig:stochastic}}
\end{figure*}

@@

@@

\subsection{Postprocessing unpaired regions: A local/global (glocal) hybrid approach}
\label{subsec:glocal_method}
Due to our simplified energy model, unpaired regions are not subject to design constraints other than the \GCContent, leading to modest probabilities for refolded design candidates to match the targeted structure. To improve these performances and test the complementarity  of our global sampling approach with previous contributions based on local search, we used the \RNAinverse software to redesign unpaired regions. We specified a constraint mask to prevent stacking base-pairs from being modified and, whenever necessary, reestablished their content {\em a posteriori}, as \RNAinverse has been witnessed to take some liberties with constraints masks. As shown in the supplementary material, this postprocessing does not drastically alter the \GCContent, so the glocal approach reasonably addresses the constrained \GCContent design problem.

@@

 \begin{figure*}[hb!]
 	\centering
	\includegraphics[width=\textwidth]{{Waldispuhl.337.fig.4}.pdf}
	\caption{Number of secondary structures per bin, according to our three clustering criteria.}
	\label{fig:bins}
 \end{figure*}

@@

\begin{figure}[hb!]
  \begin{center}
    \includegraphics[width=0.5\textwidth]{{Waldispuhl.337.fig.5}.pdf}
  \end{center}
  \caption{Overall \GCContent distribution for sequences designed using \RNAinverse, \INFORNA, \NUPACK and \frankenstein folding in the desired structure.}
  \label{fig:gcdist}
\end{figure}
